\documentclass[a4paper]{article}

\usepackage{own}

\title{Colloquium}
\date{12 September}
\author{}

\begin{document}

\maketitle

\section*{Keynote}

The keynote talked about literature reviews. They are can be thought
as publications in second layer. They are used to gather information
from the collection of publications. To be more specific,
presentation was about systematic literature reviews. It's systematic
because papers are picked and read in systematic way. That tries to
guarantee that repeated review would give the same result. It is
thus better way to do reviews. It is not recommended to do
systematic literature reviews as a master thesis.

The concept would be what is systematic literature review. It means
that process is documented. Key words and explicit inclusion and
exclusion criteria are also reported. It can also include snowballing
and study quality assessment.

Science should be transparent and reproducible. In literature reviews
there are huge amount of papers of the topic. If review would be
repeated it can be that papers used in reviews wouldn't overlap
enough and results can be different. In systematic literature review
papers are picked and results are gathered in a way that it is
transparent and reproducible.

I would create a systematic literature review about human-computer
interaction. There are different methodologies in usability testing
and other research. They can be compared and evaluated, and analyse
the results. Also there are different trends because of technological
advancements.

Language models are good at reading texts and making summaries of
texts. They are not yet as advanced that the researcher shouldn't
read any articles themselves. They can be used to analyse articles
whether to include or exclude them. They can also be used to
summarise the article.

\begin{enumerate}
  \item Topic. What was the topic of the presented thesis? ( Do not
    repeat the title.)

  \item Motivation. How did the presenter motivate the work in this
    thesis? Was the motivation convincing -- and why?

  \item Thesis contribution. What is the contribution of this thesis?
    Was the contribution described clearly?

  \item Thesis results. What are the main results of the thesis? Were
    the results presented clearly (e.g., with appropriately explained
    plots)?

  \item Relation to the given article. How is the thesis related to
    the linked article?
\end{enumerate}


\section*{Master's thesis}



\end{document}
